\frb: Properties of VLA Bursts and Implications for Overall FRB Population

### 2016-11-23 repeater-vladata.tex
obs figure looking good. working in spectral modeling

\begin{figure*}[t]
\begin{center}
\includegraphics[width=2\columnwidth]{timeline}
\caption{Summary of observing coverage during the multi-telescope observing campaign. Uncircled symbols show days with observations and circles show detections of \frb. Only the coincident Arecibo burst is currently circled (**change?**). The black dashed line shows the VLA burst detections with simultaneous coverage with other telescopes.
\label{fig:multi}}
\end{center}
\end{figure*}

@@

%\begin{table}
%\caption{Caption}
%\centering
%\begin{tabular}{llll}
%\hline
%Field       & RA          & Dec   & Lon. \\ \hline
%\end{tabular}
%\label{tab:spec}
%\end{table}

>>>>

\begin{figure*}[t]
\begin{center}
\includegraphics[width=2\columnwidth]{timeline}
\caption{Summary of observing coverage and detections of \frb\ during the multi-telescope observing campaign. Symbols show days with observations and symbols with circles show detections of \frb. Multiple circles indicate multiple burst detections, except for Arecibo, which typically has multiple detections per observing session (a detailed analysis is left for a future paper). The black dashed lines show the VLA burst detections with simultaneous coverage at other telescopes. The solid black line shows the simultaneous burst detection at VLA and Arecibo.
\label{fig:multi}}
\end{center}
\end{figure*}

@@

\begin{table}
\caption{Spectral Modeling of Bursts}
\centering
\begin{tabular}{llll}
\hline
Burst & Peak & Center & Width \\
(MJD) & (Jy *not normed yet*) & (ch) & (ch) \\ \hline
57623 & 33 & 69 & 32 \\
57633, scan 7 & 260 & 163 & 55 \\
57633, scan 13 & & & \\
57638 & & & \\
57643 & 55 & 69 & 56 \\
57645 & & & \\
57646 & & & \\
57648 & & & \\
57649 & & & \\ \hline
\end{tabular}
\label{tab:spec}
\end{table}
